Bayesian Evidence Synthesis:opioid crisis

### 2020-03-13 latex/newpaper.tex
histogram added latex

>>>>

Figure \ref{hst_ot} is the histogram of posterior samples of total overdoses per year ($O_1 + O_2 + ... + O_{12}$). 2000 samples were collected and shown as the histogram.  It is seen that the plot is bell shaped and not skewed. The total number of overdoses per year is around 10900 to 11000. [mention about credible interval] \\

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{Figures/hist_sum_ot.png}
	\caption{Histogram of posterior samples of total overdoses per year}
	\label{hst_ot}
\end{figure}
